# Unsupervised learning

Test 123

## K-means

```{r}
library(tidyverse)
library(cluster)
```

Prepare data selection.

```{r}
kmeans_data <- iris
kmeans_columns <- c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width")

kmeans_selection <- kmeans_data[kmeans_columns] %>% scale() %>% data.frame()
```

Execute silhouette analysis to determine number of centroids.

```{r}
silhouette_tries <- 10

silhouette_avg_f <- function(k_value) {
  model <- pam(x = kmeans_selection,
               k = k_value)
  model$silinfo$avg.width
}

silhouette_widths <- map_dbl(2:silhouette_tries, silhouette_avg_f)

silhouette_results <- data.frame(
  k = 2:silhouette_tries,
  sil_width = silhouette_widths
)

silhouette_results

max(silhouette_results$sil_width)

kmeans_centroids <- silhouette_results %>% 
arrange(desc(sil_width)) %>% 
  slice(1) %>% 
  pull(k)

rm(silhouette_avg_f, silhouette_tries, silhouette_widths, silhouette_results)
```

Eyecheck scree plot for the elbow to determine number of centroids.

```{r}
# scree parameters
scree_wss <- 0                 # initialize total within sum of squares error
scree_k   <- 5                 # number of clusters to cycle
scree_ns <- 10                 # number of random starts to cycle

# For 1 to 15 cluster centers
for (i in 1:scree_k) {
  km_out <- kmeans(kmeans_selection, centers = i, nstart = scree_ns)
  # Save total within sum of squares to wss variable
  scree_wss[i] <- km_out$tot.withinss
}

# Quickplot of total within sum of squares vs. number of clusters
plot(1:scree_k, scree_wss, type = "b", 
     xlab = "Number of Clusters", 
     ylab = "Within groups sum of squares")

# clean up environment
rm(i, scree_k, scree_ns, scree_wss, km_out)
```

Run k-means algorithm.

```{r}
# set random seed for reproducibility
set.seed(1337)

# run k-means with 3 centers and 20 starts
kmeans_output <- kmeans(kmeans_selection, kmeans_centroids, nstart = 20)

```

Merge the results to our original data, which is not scaled.


```{r}


kmeans_results <- kmeans_data %>% 
  mutate(Cluster = kmeans_output$cluster) %>% # Merge clusters to data
  mutate(Cluster = as.character(Cluster)) %>% # change to string for plotting asthetics
  pivot_longer(cols = c(Sepal.Length, Sepal.Width, Petal.Length, Petal.Width), names_to = "Feature", values_to = "Value") %>% 
  select(Feature, Value, Cluster)
```

Get the average value for each feature so can get some useful business information about the clusters.

```{r}
kmeans_clustermeans <- kmeans_results %>% 
  group_by(Feature, Cluster) %>% 
  summarise(
    Value = mean(Value)
  )
```

Plot a heatmap of the cluster feature means.

```{r}
# remove row names cluster and melt data
kmeans_clustermeans %>%
  
  # plot heatmap
  ggplot(aes(Cluster, Feature)) + 
  geom_tile(aes(fill = Value),
            colour = "white") +
  scale_fill_gradient(low = "white",
                      high = "#01B8AA") +
  theme(legend.position = "none",
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y=element_blank())
```

Let's clean up our environment!

```{r}
rm(kmeans_clustermeans, kmeans_data, kmeans_output, kmeans_results, kmeans_selection, kmeans_centroids, kmeans_columns)
```
