---
title: "Readme"
author: "Jiddu Alexander & Raphael Hoogvliets"
date: "16-2-2021"
output:
  md_document:
    number_sections: true
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Config {.tabset}
## Libraries
```{r Loading libraries, results="hide", message=FALSE}
# list of required packages
l_packages <- list("caret",
              "lubridate",
              "magrittr",
              "partykit",
              "pROC",
              "purrr",
              "RODBC",
              "skimr",
              "tidyverse") 

# install missing packages
if (length(setdiff(l_packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(l_packages, rownames(installed.packages())))  
}

# open required packages
lapply(l_packages, library, character.only = TRUE)

rm(l_packages)
```
## 


# Import {.tabset}
## Storage connectors
## Local connectors

# Tidy {.tabset}
## Tidy Evaluation

```{r}
library(magrittr)
```


- [rlang](https://www.tidyverse.org/blog/2019/06/rlang-0-4-0/)

```{r}
rlang_example <- function(data, var, by, ..., by_string, name) {
  data %>%
    # Quote and unquote interpolation
    dplyr::group_by({{ by }}) %>%
    dplyr::summarise(mpg_max = max({{ var }}, na.rm = TRUE)) %>% 
    # Multiple custom arguments
    dplyr::mutate(...) %>% 
    # Variable by string
    dplyr::mutate(string_var = .data[[by_string]] / 2) %>% 
    # Variable name
    dplyr::mutate({{ name }} := runif(dplyr::n()))
}

rlang_example(
  data      = mtcars, 
  var       = mpg, 
  by        = cyl, 
  mpg_max2  = mpg_max * 2, # ...
  by_string = "cyl",
  name      = runif)
```

# Transform {.tabset}
## Bla



# Model {.tabset}
## Supervised learning
###  
## Unsupervised learning {.tabset}
### K-means

#### Scree and elbow plots to determine clusters

```{r, eval=F, echo=T}
scree_selection <- data_cluster[,-1]          

# scree parameters
scree_wss <- 0                 # initialize total within sum of squares error
scree_k   <- 5                 # number of clusters to cycle
scree_ns <- 10                 # number of random starts to cycle

# For 1 to 15 cluster centers
for (i in 1:scree_k) {
  km_out <- kmeans(scree_selection, centers = i, nstart = scree_ns)
  # Save total within sum of squares to wss variable
  scree_wss[i] <- km_out$tot.withinss
}

# Quickplot of total within sum of squares vs. number of clusters
plot(1:scree_k, scree_wss, type = "b", 
     xlab = "Number of Clusters", 
     ylab = "Within groups sum of squares")

# clean up environment
rm(i, scree_selection, scree_k, scree_ns, scree_wss, km_out)
```

#### Run clustering algorithm

```{r, eval=F, echo=T}
# set random seed for reproducibility
set.seed(1337)

# run k-means with 3 centers and 20 starts
k_output <- kmeans(data_cluster_elite[,-1], 3, nstart = 20)

```

#### Merge clusters to data

```{r, eval=F, echo=T}
data_cluster_elite$cluster <- k_output$cluster
```

#### Calculate cluster means

```{r, eval=F, echo=T}
# calculate cluster means as seperate columns and bind them together
clusters <-
  cbind(
data_cluster_elite[,-1] %>% 
  subset(cluster == 1) %>% 
  colMeans(),
data_cluster_elite[,-1] %>% 
  subset(cluster == 2) %>% 
  colMeans(),
data_cluster_elite[,-1] %>% 
  subset(cluster == 3) %>% 
  colMeans()
)

# set cluster number as columnnames
colnames(clusters) = clusters["cluster",]
```

#### Plot cluster heatmap

```{r}
# remove row names cluster and melt data
plotdata_h <-clusters[-which(rownames(clusters) %in% c("cluster")), ] %>% 
  melt()

# remove columns to standardised names
colnames(plotdata_h) <- c("Var1", "Var2", "value")

# plot heatmap
ggplot(plotdata_h, aes(Var2, Var1)) + geom_tile(aes(fill = value), colour = "white") + scale_fill_gradient(low = "white", high = "#01B8AA") + theme(legend.position="none", axis.line=element_blank(), axis.ticks=element_blank(), axis.title.x=element_blank(), axis.title.y=element_blank())
```

### PCA
```{r}
library(FactoMineR)
library(skimr)
library(tidyverse)
data("poison")
skim(poison)

snippet_mca <- poison %>% 
  select_if(function(col) is.factor(col) | is.numeric(col)) %>% 
  names()


data_mcatest <- poison[snippet_mca]


data_mcatest %>% skim()


res.mca <- FAMD(data_mcatest,
                             graph=TRUE)





eig.val <- res.mca$eig
barplot(eig.val[, 2], 
        names.arg = 1:nrow(eig.val), 
        main = "Variances Explained by Dimensions (%)",
        xlab = "Principal Dimensions",
        ylab = "Percentage of variances",
        col ="steelblue")
# Add connected line segments to the plot
lines(x = 1:nrow(eig.val), eig.val[, 2], 
      type = "b", pch = 19, col = "red")

plot(res.mca, autoLab = "yes")

plot(res.mca,
     invisible = c("var", "quali.sup", "quanti.sup"),
     cex = 0.8,                                    
     autoLab = "yes")
```



## Times series {.tabset}
### Arima
## Recommendation engines
### ALS
## Tidy models

# Visualise {.tabset}
## Plotting
## Maps
## Tables

# Report {.tabset}
## Rmarkdown
## Dashboards
## Flextable

Version: flextable_0.6.2

```{r}
library(purrr) # compose function of purrr conflicts with compose from flextable
library(flextable)
library(dplyr)
library(tidyr)
library(ggplot2)
```


### Documentation:

- [https://davidgohel.github.io/flextable/](https://davidgohel.github.io/flextable/)

- [https://ardata-fr.github.io/flextable-book/](https://ardata-fr.github.io/flextable-book/)

![flextable](https://www.ardata.fr/img/illustrations/flextable_functions.svg)

### Example

```{r}
ft   <- mtcars[, c(8:9, 2, 3, 1, 6, 5, 7)] %>% arrange(vs, am, cyl) %>% 
  mutate(gg = map(seq_len(n()), ~ runif(10) *  2)) %>% 
  mutate(gg = map(gg, function(dt) {
    ggplot(mapping = aes(x = seq_along(dt), y = dt)) + geom_line() + theme_void() })) 

ftnc <- ncol(ft)

colourer <- scales::col_numeric(
  palette = c("transparent", "red"),
  domain = c(0, 500))

as_grouped_data(ft, groups = "vs") %>% 
  as_flextable() %>% 
# flextable(ft) %>% #, col_keys = names(ft)[-ftnc]) %>% 
  # set_header_labels(mpg = "MPG", wt = "WT") %>% 
  # add_header_lines(values = "Topper", top = TRUE) %>% 
  # add_header_row(values = c("", "head", "yeah"), colwidths = c(2, ftnc - 5, 3)) %>% 
  # add_footer_row(values = "Feet", colwidths = ftnc) %>% 
  set_header_df(mapping = tibble(
    col_keys = c("mpg", "cyl", "disp", "vs", "am", "wt", "list", "drat", "qsec"),
    topline  = c("Int", "Int", "dbl", "dbl", "dbl", "wt", "list", "drat", "qsec"),
    botline  = c("mpg", "cyl", "disp", "vs", "am", "wt", "list", "drat", "qsec")),
    key = "col_keys") %>%
  merge_h(part = "header") %>% 
  merge_v(j = "wt", part = "header") %>% 
  theme_alafoli() %>% 
  italic(i = 2, j = 1, part = "header") %>% 
  bold(part = "header") %>% 
  align(i = 2, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  # merge_v(j = "am", target = c("vs", "am")) %>% 
  merge_v(j = "cyl", target = c("am", "cyl")) %>% 
  color(i = c(1, 2), j = c(3, 4), color = "steelblue") %>% 
  bg(i = ~ between(wt, 3.3, 4.2), j = ~ mpg, bg = "gray") %>% 
  fontsize(part = "body", size = 9) %>% 
  bg(bg = "#e05297", part = "header") %>% 
  bg(bg = colourer, j = "disp", part = "body") %>% 
  color(color = "white", part = "header") %>% 
  bg(i = ~ !is.na(vs), bg = "#fceef5", part = "body") %>% 
  border(i = ~ !is.na(vs), border.bottom = officer::fp_border(style = "dashed"),
         border.top = officer::fp_border(style = "solid")) %>%
  align(i = ~ !is.na(vs), align = "center", part = "body" ) %>% 
  highlight(j = "wt", # grep("mpg", colnames(ft), value = TRUE),
            color = function(x) ifelse(x > 15, "yellow", "transparent")) %>% 
  fix_border_issues() %>%
  flextable::compose(j = "gg",
          value = as_paragraph(
            gg_chunk(value = gg, width = 1, height = 0.1)
            )) %>% 
  flextable::compose(j = "drat",
          value = as_paragraph(
            minibar(value = drat, max = max(drat, na.rm = TRUE), height = .15)
            ),
  part = "body") %>% 
  flextable::compose(j = "qsec",
          value = as_paragraph(
            linerange(value = qsec, max = max(qsec, na.rm = TRUE), height = .15)
            ),
  part = "body")
  # flextable::compose(j = "list", value = as_paragraph(
  #   plot_chunk(value = list, type = "line", col = "pink",
  #              width = 1.5, height = .4, free_scale = TRUE)
  # ))
# htmltools_value() # For shiny uiOutput
```

### Shiny

```{r, eval=FALSE}
library(shiny)
library(flextable)
library(dplyr)

dat <- mtcars %>%
  mutate(car = rownames(.)) %>%
  select(car, everything())

ui <- fluidPage(
  titlePanel("mtcars"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("mpg", "mpg Limit", min = 11, max = 33, value = 20),
      actionButton("browse", "Browser")
    ),
    mainPanel(uiOutput("mtcars_ft"))
  )
)

server <- function(input, output) {
  observeEvent(input$browse, { browser() })
  
  output$mtcars_ft <- renderUI({
    req(input$mpg)
    filter(dat, mpg <= input$mpg) %>%
      flextable() %>%
      theme_vader() %>%
      autofit() %>%
      htmltools_value()
  })
}

# Run the application
shinyApp(ui = ui, server = server)
```

